---
title: "Drift_QAQC"
author: "Catarina Pien"
date: "April 20, 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
YBFMP Drift Invertebrate Data 1998 - 2022
## modified 2023/2024 by L.Vance for publishing update

```{r set-options, echo=FALSE, cache=FALSE}

options(width = 10000)
```

## Setup 

1.Setup and Download Libraries

```{r setup, results=FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

library(tidyverse)
library(gridExtra) # combine plots
library(stringr)
library(readr)
library(lubridate)
library(plotly)
library(viridis)
library(kableExtra)
library(tidylog)
```

2.Load Data, Check Variable Types

```{r load, results = FALSE, warning = FALSE, message = FALSE}
# Load data - several tables
phys <- read_csv("drift data/LT_phys_qc_20240118.csv")
catch <- read_csv("drift data/DriftCatchDataAccess_20240119.csv")
catch2 <- read_csv("drift data/DriftLabExcelData_20240430.csv", skip=1)
samp <- read_csv("drift data/DriftInvertSampAccess_20240119.csv")
samp2 <- read_csv("drift data/DriftSampExcelData.csv", skip=1)
tax <- read_csv("drift data/DriftTaxonomy.csv")
wy <- read_csv("WaterYearType_CDEC.csv") 
inundation <- read_csv("Yolo_Bypass_Inundation_1998-2022.csv")
#inv_tax_2 <- read_csv("Data/TblInvertsLookUpV2.csv")

```

3. Rename variables
```{r filter, results = FALSE, message = FALSE, warning = FALSE}

samp <- samp %>% 
  rename(FlowMeterStart = `DriftStartMeter`,
         FlowMeterEnd = `DriftEndMeter`) %>%
  select(-c(`EnteredBy`, `QA/QC'dBy`, StartTime, StopTime))
str(samp)

catch2 <- catch2 %>%
  filter(!(is.na(`Measuring program short name`))) %>%
  rename(Count = `Value...11`,
         LifeStage = `Value...12`,
         TaxonName = Observable,
         Date = `Sampling Event Date`,
         Time = `Sampling Event Time`,
         Station = `Sampling Area Number`,
         SAMCode = `Sampling Event Number`,
         SampleID = `Sample ID`,
         LabComments = lab_comments) %>%
  select(-c(`Measuring program short name`, `Observation Type Short Name`,
            SAMCode))

samp2 <- samp2 %>%
  filter(!(is.na(`Measuring program short name`))) %>%
  rename(FlowMeterStart = `Flow Meter Start`,
         FlowMeterEnd = `Flow Meter End`,
         Date = `Sampling Event Date`,
         Time = `Sampling Event Time`,
         Station = `Sampling Area Number`,
         SAMCode = `Sampling Event Number`) %>%
  select(-c(`Observation Area Number`, `Spot Code (original/duplicate)`, `...27`, `...28`,
            `...29`, `...30`, `...31`, `...32`,
            `Spot Number`, `Flow Meter Start (50)`, `Flow Meter End (50)`,
            `Entered by`, `QAQC'd by`, `...6`, `Measuring program short name`,
            SAMCode))

#check df structure
str(phys)
str(catch)
str(samp)
str(samp2)
str(catch2)

```



3.Add and change date/time formats
```{r filter, results = FALSE, message = FALSE, warning = FALSE}

#phys looks like it's in the correct format already post qa/qc

catch2$Date<-as.Date(catch2$Date,"%m/%d/%Y")
catch2$Year <- year(catch2$Date)
catch2$Month <- month(catch2$Date)
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
catch2$MonthAbb <- mymonths[catch2$Month ]
catch2$Datetime = paste(catch2$Date, catch2$Time)
catch2$Datetime <- ymd_hm(catch2$Datetime)
catch2$Time <- strptime(catch2$Time, format = "%H:%M", tz = "") %>%
  strftime(catch2$Time, format = "%H:%M:%S", tz = "", usetz = FALSE)
catch2$Time <- hms::as_hms(catch2$Time)

samp2$Date<-as.Date(samp2$Date,"%m/%d/%Y")
samp2$Year <- year(samp2$Date)
samp2$Month <- month(samp2$Date)
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
samp2$MonthAbb <- mymonths[samp2$Month ]
samp2$Datetime = paste(samp2$Date, samp2$Time)
samp2$Datetime <- ymd_hm(samp2$Datetime)
samp2$Time <- strptime(samp2$Time, format = "%H:%M", tz = "") %>%
  strftime(samp2$Time, format = "%H:%M:%S", tz = "", usetz = FALSE)
samp2$Time <- hms::as_hms(samp2$Time)

inundation <- inundation %>%
  rename(Date = Dates)
inundation$Date<-as.Date(inundation$Date,"%m/%d/%Y")

#check data types again
str(phys)
str(catch)
str(samp)
str(samp2)
str(catch2)
str(inundation)

```

4. Merge data tables that came from Excel, for ease of combining with Access, create eventID
```{r}

#first create event_id
catch2 <- catch2 %>%
  mutate(event_id = paste0(Station, "_", Datetime)) %>%
  relocate(event_id, Datetime)

samp2 <- samp2 %>%
  mutate(event_id = paste0(Station, "_", Datetime)) %>%
  relocate(event_id, Datetime)

#join data frames and select for data through end of 2022
samp_catch2 <- left_join(samp2, catch2) %>%
  filter(Date < "2023-01-01")
str(samp_catch2)

#ensure column types match for joining with Access data
samp_catch2$Date <- as.Date(samp_catch2$Date)
samp_catch2 <- samp_catch2 %>%
  mutate(FlowMeterEnd = as.numeric(FlowMeterEnd))

#combine with phys data in prep to merge with access data before flowmeter values
#rename some columns, remove duplicate columns

samp_catch_phys2 <- left_join(samp_catch2, phys, by = c("event_id","Datetime", "Station", "Date", "Time",
                                                        "Year", "Month", "MonthAbb")) %>%
  select(-c("FlowMeterStart.y", "FlowMeterEnd.y", "MeterSetTime", "FlowMeterSpeed", 
            "Observation Area Name", "Physical Data ID", "Sampling Altered", "ConditionCode")) %>%
  rename(FlowMeterStart = "FlowMeterStart.x",
         FlowMeterEnd = "FlowMeterEnd.x",
         FlowMeterSpeed = "Flow Meter Speed",
         SetTime = "Set Time",
         Field_Comments = "Field Comments",
         SampleVolume = "Sample Volume",
         SubsampleNumber = "Subsample Number",
         SlideCount = "Slide Count",
         ConditionCode = "Condition Code") %>%
  select(-c(Field_Comments))

```


5. Merge data tables, calculate Flowmeter difference, rearrange variables
```{r merge, message = FALSE, warning = FALSE}
# Merge datasets for CPUE variables
# tax <- full_join(inv_tax, inv_tax_2, by = "OrganismID")

samp_catch <- left_join(samp, catch)

#rename and remove columns from join
# 04-22-2019 onward was entered into Excel, not Access
samp_catch_phys0 <- left_join(phys, samp_catch, by = "PhysicalDataID") %>%
  filter(!is.na(Station)) %>%
  filter(Date < "2019-04-22") 
notjoinedPhysDataID <- anti_join(phys, samp_catch, by = "PhysicalDataID")

#clean up and rename some columns
samp_catch_phys0 <- samp_catch_phys0 %>%
  select(-c("ConditionCode.x", "MeterSetTime", "FlowMeterStart.x", "FlowMeterEnd.x",
            "FlowMeterSpeed.x", "FieldComments.x")) %>%
  rename(FlowMeterStart = "FlowMeterStart.y",
         FlowMeterEnd = "FlowMeterEnd.y",
         FlowMeterSpeed = "FlowMeterSpeed.y",
         ConditionCode = "ConditionCode.y",
         FieldComments = "FieldComments.y")

# For second part 2019, merge phys-samp, then add catch.
# For the additional data

catch2019 <- catch2 %>%
  filter(Date > "2019-04-10" & Date < "2020-02-01")

phys2019 <- phys %>%
  filter(Date > "2018-12-31" & Date < "2020-01-01") %>%
  select(-c(FieldComments))
#fieldcomments removed for 2019 since all NA and the comments are in a diff comments column

phys_samp <- left_join(phys2019, samp, by = "PhysicalDataID")%>%
  select(-c("ConditionCode.x", "MeterSetTime", "FlowMeterStart.x", "FlowMeterEnd.x",
            "FlowMeterSpeed.x")) %>%
  rename(FlowMeterStart = "FlowMeterStart.y",
         FlowMeterEnd = "FlowMeterEnd.y",
         FlowMeterSpeed = "FlowMeterSpeed.y",
         ConditionCode = "ConditionCode.y")

gap <- left_join(phys_samp, catch2019)

#combine the 2019 data with the rest of the access data
samp_catch_phys <- bind_rows(samp_catch_phys0, gap)

#Now combine these two files to then continue with qa/qc
sampcatchphysMerge <- bind_rows(samp_catch_phys, samp_catch_phys2) %>%
  relocate(event_id, Datetime)

#create exported joined data file for ease of publishing data in future
write_csv(sampcatchphysMerge, paste("R_write/SamplingDrift1998-2022.csv"))

# All samplings - remove catch info and find unique entries
sampUnique <- sampcatchphysMerge %>%
  unique() %>%
  arrange(Datetime)

```


```{r}
# In the future, figure out what to do with lab comments, which for drift are at the observable level. If they never include lab comments relative to sample quality, leave these out. If they are included, need to add !is.na(LabComments to the SamplingQAQC command.)
sampA <- sampcatchphysMerge %>%
  select(-c(WeatherCode:Turbidity, Year:Comment_PQC,  TaxonName:LifeStage)) %>%
  unique() %>%
  arrange(Datetime)
```

Add Water Year and Water Year "Class" (W = W, D/C = D, AN/BN = A), calculate Flowdiff
```{r}
samp_catch_physMerge <- sampcatchphysMerge %>%
  mutate(WY = ifelse(Month >9, Year + 1, Year)) %>%
  left_join(wy, by = "WY") %>%
  select(-c(Index, WYType)) %>%
  mutate(Flowdiff = FlowMeterEnd-FlowMeterStart)
```

## QAQC 

* QC Flags: Blank = no issues/1 = Comment but deemed Acceptable/ 2 = Suspect/ 3 = Highly Suspect
* Flag_SAMP: Sampling issues
* Flag_LAB: Lab issues
* Flag_FM: Flowmeter
* Flag_CPUE: CPUE

### QAQC Sampling and Lab issues

6. Export sampling table
7. Look at field sampling comments
8. Flag comments reflecting poor data quality (Flag_SAMP)
9. Add comment about what was flagged
    * FMMISSING if lacking flowmeter values
    * SAMP for other sampling issues 
    * Leave blank if no issues
10. Look at lab comments and flag if poor data quality
11. Add Comment_LAB
    * LAB if lab issues (e.g. unable to meet meso or microtally)
    * Leave blank if no issues

* This part is manual. Think about how to make this codeable, change our condition code flags or add a flag as part of data entry? 
* The following section creates blank columns before creating the csv to manually filter through comments and add appropriate notation before reading the file back in at step 12

```{r}
SamplingQAQC <- filter(sampUnique, !is.na(FieldComments) | ConditionCode>1 | !is.na(LabComments))
SamplingQAQC$Flag_SAMP <-  ""
SamplingQAQC$Comment_SAMP <-""
SamplingQAQC$Flag_LAB <- ""
SamplingQAQC$Comment_LAB <- ""
today <- today()
write.csv(SamplingQAQC, paste("R_write/SamplingQAQC_", today, ".csv"))

```

12. Read edited file in

```{r}
SamplingQAQC_fill <- read.csv("R_write/SamplingQAQC_ Notated_20240430 .csv")
SamplingQAQC_fill_s <- SamplingQAQC_fill %>%
  select(c(event_id, PhysicalDataID, Flag_SAMP, Comment_SAMP, Flag_LAB, Comment_LAB))
```


### QAQC Flowmeters

13. Inundation data

    This data comes from Water Data Library, Stations at Fremont Weir (A02170) and I Street Bridge . If Stage Height > 32ft at Fremont Weir, Inundation = TRUE. If there is no data at Fremont Weir, and Stage Height > 17 ft at I Street Bridge, Inundation = TRUE. There was also 2 days of lag time added in for inundation (variable Inundation2). 
    
* Inundation used to QA/QC STTD data. 

```{r}
inundation <- inundation %>%
  mutate(Month = month(Date),
         Year = year(Date),
         WY = ifelse(Month > 9, Year + 1, Year))

# Modify sample table to include Flowdiff
samp3 <-sampUnique %>%
  mutate(Flowdiff = FlowMeterEnd-FlowMeterStart,
         Flowdiff_s = Flowdiff/SetTime) 

# merged inundation and sampling
inundation_flow <- left_join(samp3, inundation, by = "Date") %>%
    filter(Flowdiff<100000) %>%
  filter(Station == "STTD") %>%
  mutate(Flowdiff_s = Flowdiff/SetTime,
         Inundation_n = ifelse(Inundation == "TRUE", 40000, 0))

# all inundation
inundation2 <- inundation %>%
  mutate(Inundation_n = ifelse(Inundation == "TRUE", 40000, 0),
         Inundation_n_low = ifelse(Inundation == "TRUE", 5000,0))

# Plot - only inundation events that correspond with sampling date
inplot1 <- ggplot(inundation_flow) + 
  geom_point(aes(x = Date, y = Flowdiff)) + 
  geom_col(aes(x = Date, y = Inundation_n), fill = "blue", linewidth = 2) + 
  labs(title = "Flowdiff with Inundation events corresponding with sample dates") +
  facet_grid(Station~.) +
  theme_bw()

ggplotly(inplot1)

# Plot - All inundation events
inplot2 <- ggplot() +
  geom_point(data = inundation_flow, aes(x = Date, y = Flowdiff)) +
  labs(title = "Flowdiff with all Inundation") +
  geom_col(data = inundation2, aes(x = Date, y = Inundation_n), fill = 
                 "blue", alpha = 0.6) + theme_bw()
ggplotly(inplot2)

inplot3 <- ggplot() +
  geom_point(data = inundation_flow, aes(x = Date, y = Flowdiff_s)) +
  labs(title = "Standardized Flowdiff with all Inundation") +
  geom_col(data = inundation2, aes(x = Date, y = Inundation_n_low), fill = 
                 "blue", alpha = 0.6) + theme_bw()

grid.arrange(inplot1, inplot2, inplot3, nrow = 3)


# Allow 10 days after last "inundation=TRUE" to also count as inundated. Merge with sample data. 
inundation4 <- inundation %>%
  mutate(Inundation2 = ifelse(lead(Inundation, 10) == "TRUE", "TRUE", Inundation)) %>%
  select(c(Date, Month:Inundation2))

samp_catch_phys <- left_join(samp_catch_physMerge, inundation4)%>%
  select(-SampleID)
#move removing sampleID to beginning for next publishing update
```

14. Look at distribution of flowmeter values
```{r warning = FALSE, message = FALSE}
# Histogram of values
samp_catch_phys$Month <- ordered(samp_catch_phys$Month)
FlowHist <- ggplot(samp_catch_phys, aes(Flowdiff)) + geom_histogram() +
  facet_wrap(~Station) + theme_bw()

# SHR vs STTD boxplot
FlowBox <- ggplot(samp_catch_phys) + geom_boxplot(aes(x = Station, y = Flowdiff)) + theme_bw()

# SHR vs STTD boxplot by month
FlowBoxMonth <- ggplot(samp_catch_phys) + geom_boxplot(aes(x = Month, y = Flowdiff, fill = Month)) + facet_wrap(~Station) + scale_fill_viridis(discrete = TRUE) + theme_bw() 

# SHR vs STTD boxplot by year
FlowBoxYear <- ggplot(samp_catch_phys) + geom_boxplot(aes(x = ordered(WY), y = Flowdiff, fill = ordered(WY))) + facet_wrap(~Station) + theme_bw() 

# SetTime vs Flowdiff by station and month
FlowPoint <- ggplot(samp_catch_phys, aes(x = SetTime, y = Flowdiff, color = Month)) + geom_point(size = 3) + facet_wrap(~Station) + theme_bw()

# SetTime vs Flowdiff by station and flowmeter type
FlowPoint2 <- ggplot(samp_catch_phys, aes(x = SetTime, y = Flowdiff, color = FlowMeterSpeed)) + geom_point(size = 3) + facet_wrap(~Station) + theme_bw() + scale_color_viridis(discrete = TRUE) 


grid.arrange(FlowBox, FlowHist)
grid.arrange(FlowBoxMonth, FlowBoxYear)
grid.arrange(FlowPoint, FlowPoint2)
```

15. Change obvious flowmeter values
```{r QAQC-Flowmeters}
# Change known incorrect values
# Change FlowMeterStart and FlowMeterEnd, Recalculate Flowdiff
# SamplingID = 47736 Switched FlowMeterStart and FlowMeterEnd 
#account for different rotors spinning different directions by using absolute value for flowdiff
#flowmeter maxes out at 999,999 then starts over at 0. For any values where value is 999,xxx and 000,xxx, find
# difference between 999,999 and 999,xxx then add the 000xxx (SHR_2022-09-06 07:29:00)
check <- samp_catch_phys %>% filter(Flowdiff < 0)

samp_catch_phys$FlowMeterStart[samp_catch_phys$PhysicalDataID==1727] <- 573926
samp_catch_phys$FlowMeterEnd[samp_catch_phys$PhysicalDataID==1727] <- 581200
samp_catch_phys$Flowdiff[samp_catch_phys$PhysicalDataID==1727] <- 581200-573926

samp_catch_phys$FlowMeterStart[samp_catch_phys$InvertDataID==978] <- 788767
samp_catch_phys$FlowMeterEnd[samp_catch_phys$InvertDataID==978] <- 	795100
samp_catch_phys$Flowdiff[samp_catch_phys$InvertDataID==978] <- 795100-788767

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2020-11-30 10:13:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2020-11-30 10:13:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-04-27 09:33:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-04-27 09:33:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-05-24 09:44:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-05-24 09:44:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-05-25 09:16:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-05-25 09:16:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-06-07 09:02:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-06-07 09:02:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-06-09 09:37:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-06-09 09:37:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-06-21 08:58:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-06-21 08:58:00"])


samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-06-22 09:17:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-06-22 09:17:00"])


samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-07-06 09:03:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-07-06 09:03:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-08-31 08:06:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-08-31 08:06:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-08-31 11:06:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-08-31 11:06:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-09-14 07:51:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-09-14 07:51:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-09-14 11:34:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-09-14 11:34:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-09-28 08:10:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-09-28 08:10:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-09-28 11:25:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-09-28 11:25:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-10-12 08:24:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-10-12 08:24:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-10-13 11:07:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-10-13 11:07:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-10-18 08:23:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-10-18 08:23:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-10-19 08:13:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-10-19 08:13:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-11-15 10:05:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-11-15 10:05:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-11-16 09:48:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-11-16 09:48:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-11-29 09:19:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-11-29 09:19:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-11-30 09:30:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-11-30 09:30:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-12-13 09:21:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-12-13 09:21:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-12-14 10:25:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-12-14 10:25:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-12-27 10:18:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2021-12-27 10:18:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-12-28 10:48:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2021-12-28 10:48:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-01-11 09:14:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-01-11 09:14:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-01-10 10:54:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-01-10 10:54:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-01-25 09:28:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-01-25 09:28:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-01-24 12:33:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-01-24 12:33:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-02-08 09:38:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-02-08 09:38:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-02-07 10:17:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-02-07 10:17:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-02-22 09:52:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-02-22 09:52:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-02-23 10:01:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-02-23 10:01:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-03-14 09:27:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-03-14 09:27:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-03-15 08:37:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-03-15 08:37:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-03-28 08:01:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-03-28 08:01:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-03-29 09:00:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-03-29 09:00:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-04-11 08:05:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-04-11 08:05:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-04-12 08:26:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-04-12 08:26:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-04-25 08:07:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-04-25 08:07:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-04-26 08:55:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-04-26 08:55:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-05-09 10:39:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-05-09 10:39:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-05-10 08:34:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-05-10 08:34:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-05-23 10:12:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-05-23 10:12:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-06-06 07:24:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-06-06 07:24:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-06-07 08:17:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-06-07 08:17:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-06-20 08:25:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-06-20 08:25:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-06-21 08:09:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-06-21 08:09:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-07-12 09:31:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-07-12 09:31:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-07-13 09:07:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-07-13 09:07:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-07-26 09:10:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-07-26 09:10:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-07-27 08:59:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-07-27 08:59:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-08-09 09:02:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-08-09 09:02:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-08-10 09:23:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-08-10 09:23:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-09-06 07:29:00"] <- abs((999999-samp_catch_phys$FlowMeterStart[samp_catch_phys$event_id== "SHR_2022-09-06 07:29:00"]) + samp_catch_phys$FlowMeterEnd[samp_catch_phys$event_id== "SHR_2022-09-06 07:29:00"])

  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-09-07 06:20:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-09-07 06:20:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-09-20 08:57:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-09-20 08:57:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-09-21 09:24:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-09-21 09:24:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-10-04 08:25:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-10-04 08:25:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-10-18 09:19:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-10-18 09:19:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-10-19 08:42:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-10-19 08:42:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-11-01 08:57:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-11-01 08:57:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-11-14 10:27:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-11-14 10:27:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-11-15 10:08:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-11-15 10:08:00"])
  
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-11-29 10:22:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-11-29 10:22:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-12-13 10:21:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-12-13 10:21:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-12-12 09:27:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-12-12 09:27:00"])  
    
samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-12-27 11:21:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "SHR_2022-12-27 11:21:00"])

samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-12-28 10:16:00"] <- abs(samp_catch_phys$Flowdiff[samp_catch_phys$event_id== "STTD_2022-12-28 10:16:00"])  



#fix the same flow meter values in samp3

samp3$FlowMeterStart[samp3$PhysicalDataID==1727] <- 573926
samp3$FlowMeterEnd[samp3$PhysicalDataID==1727] <- 581200
samp3$Flowdiff[samp3$PhysicalDataID==1727] <- 581200-573926

samp3$FlowMeterStart[samp3$InvertDataID==978] <- 788767
samp3$FlowMeterEnd[samp3$InvertDataID==978] <- 	795100
samp3$Flowdiff[samp3$InvertDataID==978] <- 795100-788767

samp3$Flowdiff[samp3$event_id== "SHR_2020-11-30 10:13:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2020-11-30 10:13:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-04-27 09:33:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-04-27 09:33:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-05-24 09:44:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-05-24 09:44:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-05-25 09:16:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-05-25 09:16:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-06-07 09:02:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-06-07 09:02:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-06-09 09:37:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-06-09 09:37:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-06-21 08:58:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-06-21 08:58:00"])


samp3$Flowdiff[samp3$event_id== "STTD_2021-06-22 09:17:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-06-22 09:17:00"])


samp3$Flowdiff[samp3$event_id== "STTD_2021-07-06 09:03:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-07-06 09:03:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-08-31 08:06:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-08-31 08:06:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-08-31 11:06:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-08-31 11:06:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-09-14 07:51:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-09-14 07:51:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-09-14 11:34:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-09-14 11:34:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-09-28 08:10:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-09-28 08:10:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-09-28 11:25:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-09-28 11:25:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-10-12 08:24:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-10-12 08:24:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-10-13 11:07:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-10-13 11:07:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-10-18 08:23:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-10-18 08:23:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-10-19 08:13:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-10-19 08:13:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-11-15 10:05:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-11-15 10:05:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-11-16 09:48:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-11-16 09:48:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-11-29 09:19:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-11-29 09:19:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-11-30 09:30:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-11-30 09:30:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-12-13 09:21:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-12-13 09:21:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-12-14 10:25:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-12-14 10:25:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2021-12-27 10:18:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2021-12-27 10:18:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2021-12-28 10:48:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2021-12-28 10:48:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-01-11 09:14:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-01-11 09:14:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-01-10 10:54:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-01-10 10:54:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-01-25 09:28:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-01-25 09:28:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-01-24 12:33:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-01-24 12:33:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-02-08 09:38:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-02-08 09:38:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-02-07 10:17:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-02-07 10:17:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-02-22 09:52:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-02-22 09:52:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-02-23 10:01:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-02-23 10:01:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-03-14 09:27:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-03-14 09:27:00"])
  
samp3$Flowdiff[samp3$event_id== "SHR_2022-03-15 08:37:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-03-15 08:37:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-03-28 08:01:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-03-28 08:01:00"])
  
samp3$Flowdiff[samp3$event_id== "SHR_2022-03-29 09:00:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-03-29 09:00:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-04-11 08:05:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-04-11 08:05:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-04-12 08:26:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-04-12 08:26:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-04-25 08:07:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-04-25 08:07:00"])  
    
samp3$Flowdiff[samp3$event_id== "SHR_2022-04-26 08:55:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-04-26 08:55:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-05-09 10:39:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-05-09 10:39:00"])
  
samp3$Flowdiff[samp3$event_id== "SHR_2022-05-10 08:34:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-05-10 08:34:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-05-23 10:12:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-05-23 10:12:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-06-06 07:24:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-06-06 07:24:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-06-07 08:17:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-06-07 08:17:00"])  
    
samp3$Flowdiff[samp3$event_id== "SHR_2022-06-20 08:25:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-06-20 08:25:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-06-21 08:09:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-06-21 08:09:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-07-12 09:31:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-07-12 09:31:00"])
  
samp3$Flowdiff[samp3$event_id== "SHR_2022-07-13 09:07:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-07-13 09:07:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-07-26 09:10:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-07-26 09:10:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-07-27 08:59:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-07-27 08:59:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-08-09 09:02:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-08-09 09:02:00"])  
    
samp3$Flowdiff[samp3$event_id== "SHR_2022-08-10 09:23:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-08-10 09:23:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-09-06 07:29:00"] <- abs((999999-samp3$FlowMeterStart[samp3$event_id== "SHR_2022-09-06 07:29:00"]) + samp3$FlowMeterEnd[samp3$event_id== "SHR_2022-09-06 07:29:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-09-07 06:20:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-09-07 06:20:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-09-20 08:57:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-09-20 08:57:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-09-21 09:24:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-09-21 09:24:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-10-04 08:25:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-10-04 08:25:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-10-18 09:19:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-10-18 09:19:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-10-19 08:42:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-10-19 08:42:00"])
  
samp3$Flowdiff[samp3$event_id== "SHR_2022-11-01 08:57:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-11-01 08:57:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-11-14 10:27:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-11-14 10:27:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-11-15 10:08:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-11-15 10:08:00"])
  
samp3$Flowdiff[samp3$event_id== "STTD_2022-11-29 10:22:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-11-29 10:22:00"])  
    
samp3$Flowdiff[samp3$event_id== "STTD_2022-12-13 10:21:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-12-13 10:21:00"])

samp3$Flowdiff[samp3$event_id== "SHR_2022-12-12 09:27:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-12-12 09:27:00"])  
    
samp3$Flowdiff[samp3$event_id== "SHR_2022-12-27 11:21:00"] <- abs(samp3$Flowdiff[samp3$event_id== "SHR_2022-12-27 11:21:00"])

samp3$Flowdiff[samp3$event_id== "STTD_2022-12-28 10:16:00"] <- abs(samp3$Flowdiff[samp3$event_id== "STTD_2022-12-28 10:16:00"])



```

16. Merge data with lab/sampling QAQC 
    * Replace NA with blank
```{r}
FM_Samp <- left_join(samp_catch_phys, SamplingQAQC_fill_s, by = "event_id") %>%
  mutate(Flag_SAMP = replace(Flag_SAMP, is.na(Flag_SAMP), "" ),
         Comment_SAMP = replace(Comment_SAMP, is.na(Comment_SAMP), ""),
         Flag_LAB = replace(Flag_LAB, is.na(Flag_LAB), ""),
         Comment_LAB = replace(Comment_LAB, is.na(Comment_LAB), "")) %>%
  select(-c(PhysicalDataID.y))%>%
  rename(PhysicalDataID = "PhysicalDataID.x")
```

17. Make a table of summarized flowmeter values for different conditions
    * Use Flowdiff/Settime to look for outliers
    * Use inundation as a grouping variable for STTD but not SHR
    
STTD
```{r message = FALSE, warning = FALSE}
### Table of values
# Calculate median, lower and upper ranges for each day
Flow.sum.STTD <- samp3 %>%
  left_join(inundation4) %>%
  left_join(wy)%>%
  filter(!is.na(Flowdiff), !is.na(Inundation2), Station=="STTD") %>%
  mutate(Flow_s = Flowdiff/SetTime) %>%
  group_by(Station, FlowMeterSpeed, WYClass, Inundation2) %>%
  summarize(n= n(),
            min.Flowdiff = min(Flowdiff),
            max.Flowdiff = max(Flowdiff),
            median.Flowdiff = median(Flowdiff),
            min.Flowdiff_s = min(Flow_s),
            max.Flowdiff_s = max(Flow_s),
            median.Flowdiff_s = median(Flow_s),
            Flow_Q1 = quantile(Flowdiff, probs = 0.25),
            Flow_Q3 = quantile(Flowdiff, probs = 0.75),
            Flow_UL = Flow_Q3 + 1.5 * (Flow_Q3-Flow_Q1),
            Flow_s_Q1 = quantile(Flow_s, probs = 0.25), 
            Flow_s_Q3 = quantile(Flow_s, probs = 0.75),
            Flow_s_UL = Flow_s_Q3 + 1.5 * (Flow_s_Q3-Flow_s_Q1),
            Flow_s_MAD = mad(Flow_s))


Flow.sum.STTD %>%
  kbl() %>%
  kable_styling()


```

Sherwood
```{r message = FALSE, warning = FALSE}
Flow.sum.SHR <- samp3 %>%
  left_join(inundation4) %>%
  left_join(wy)%>%
  mutate(Flow_s = Flowdiff/SetTime) %>%
  group_by(Station, FlowMeterSpeed, WYClass) %>%
  filter(!is.na(Flowdiff), Station == "SHR") %>%
  summarize(n= n(),
            min.Flowdiff = min(Flowdiff),
            max.Flowdiff = max(Flowdiff),
            median.Flowdiff = median(Flowdiff),
            min.Flowdiff_s = min(Flow_s),
            max.Flowdiff_s = max(Flow_s),
            median.Flowdiff_s = median(Flow_s),
            Flow_Q1 = quantile(Flowdiff, probs = 0.25),
            Flow_Q3 = quantile(Flowdiff, probs = 0.75),
            Flow_UL = Flow_Q3 + 1.5 * (Flow_Q3-Flow_Q1),
            Flow_s_Q1 = quantile(Flow_s, probs = 0.25), 
            Flow_s_Q3 = quantile(Flow_s, probs = 0.75),
            Flow_s_UL = Flow_s_Q3 + 1.5 * (Flow_s_Q3-Flow_s_Q1),
            Flow_s_MAD = mad(Flow_s))

Flow.sum.SHR %>%
    kbl() %>%
  kable_styling()
```

18. Apply outlier definitions to data

* Merge table (above) with rest of the data so averages are based on each individual collected sample and not multiplied for each organism in a sample. 
* Calculate modified Z score, then label each row as outlier = Tukey, MAD, or BOTH.
* Do this separately for STTD and SHR
```{r}
Flow.outlier.STTD <- left_join(FM_Samp, Flow.sum.STTD) %>%
    mutate(Flow_s = Flowdiff/SetTime) %>%
  filter(!is.na(Flowdiff), !is.na(Inundation2), Station=="STTD") %>%
  group_by(Station, FlowMeterSpeed, WYClass) %>%
  mutate(Flow_modZ = abs(0.6745*(Flow_s - median.Flowdiff_s)/Flow_s_MAD),
         Flow_Outlier = ifelse((Flow_s > Flow_UL) & Flow_modZ > 3.5, "Both", ifelse(Flow_s > Flow_UL, "Tukey", ifelse(Flow_modZ > 3.5, "MAD", 
            "None"))))

summary(factor(Flow.outlier.STTD$Flow_Outlier))

Flow.outlier.SHR <- left_join(FM_Samp, Flow.sum.SHR) %>%
  mutate(Flow_s = Flowdiff/SetTime) %>%
  filter(!is.na(Flowdiff),  Station=="SHR") %>%
  group_by(Station, FlowMeterSpeed, WYClass) %>%
  mutate(Flow_modZ = abs(0.6745*(Flow_s - median.Flowdiff_s)/Flow_s_MAD),
         Flow_Outlier = ifelse((Flow_s > Flow_UL) & Flow_modZ > 3.5, "Both", ifelse(Flow_s > Flow_UL, "Tukey", ifelse(Flow_modZ > 3.5, "MAD", 
            "None"))))

summary(factor(Flow.outlier.SHR$Flow_Outlier))
```

19. Plot outliers - STTD
```{r}
FlowBoxMonth1a <- ggplot(Flow.outlier.STTD) + geom_boxplot(aes(x = WYClass, y = Flow_s)) +  scale_fill_viridis(discrete = TRUE) + theme_bw() 
ggplotly(FlowBoxMonth1a)


outlierWY1a <- ggplot(Flow.outlier.STTD, aes(x = WYClass, y = Flow_s, color = Flow_Outlier)) + geom_point(size = 2.5, alpha = 0.5) +
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))


outlierMonth1a <- ggplot(Flow.outlier.STTD, aes(x = Month, y = Flow_s, color = Flow_Outlier)) + geom_point(size = 2.5, alpha = 0.5) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

grid.arrange(FlowBoxMonth1a, outlierWY1a, outlierMonth1a)
```

Sherwood outliers
```{r}
FlowBoxMonth1b <- ggplot(Flow.outlier.SHR) + geom_boxplot(aes(x = WYClass, y = Flow_s)) +  scale_fill_viridis(discrete = TRUE) + theme_bw() 
ggplotly(FlowBoxMonth1b)


outlierWY1b <- ggplot(Flow.outlier.SHR, aes(x = WYClass, y = Flow_s, color = Flow_Outlier)) + geom_point(size = 2.5, alpha = 0.5) +   
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))


outlierMonth1b <- ggplot(Flow.outlier.SHR, aes(x = Month, y = Flow_s, color = Flow_Outlier)) + geom_point(size = 2.5, alpha = 0.5) +   
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

grid.arrange(FlowBoxMonth1b, outlierWY1b, outlierMonth1b)

```


Merge two files
```{r}
Flow.outlier <- rbind(Flow.outlier.SHR, Flow.outlier.STTD)
```


20. Flowmeter Flags and New Flowdiff calculated

Cutoffs based on looking at plots and Upper limits calculated above. 

Flag   | Description                | Outlier                   | Flowdiff
Flag 3 | Highly Suspect             | Both                      | < 200 or >= 70000 or >= 50000 if inundation = FALSE
Flag 2 | Suspect                    | Tukey or MAD but not Both | 200-999 
Flag 1 | Acceptable                 |                           | 
No flag| Acceptable                 | None                      | 1000-59999

21. Add comment about what was flagged (FM for flowmeter-related)
22. Calculate replacement values where Flag_FM = 3 or Comment_SAMP = FM
  * Replacement values are median standardized flowdiff * settime based on groupings of Station, Flowmeter Speed, Water Year Class

```{r Flag-Replace-Flowmeters}
################## Flag Flowmeter data: Flag_QC1 ############################
# Mutate QC Flags 
# Conditions for Flag 3: Outlier = Both | Flowdiff < 200 | Flowdiff >= 50000 when no inundation | Flowdiff >= 70000
# Conditions for Flag 2: Outlier = Tukey | Outlier = MAD (but not Both) |Flowdiff between 200-999 
# Conditions for Flag 1: Acceptable data

# If Flag 3, calculate FlowdiffAdj = median.Flowdiff_s * SetTime

FlowmeterQAQC <- Flow.outlier %>%
  filter(!is.na(Flowdiff), Flow_modZ>=0.00000001) %>%
  mutate(Flag_FM = ifelse(Flow_Outlier=="Both" | Flowdiff < 200 | (Flowdiff >= 50000 & Inundation2 ==FALSE) | Flowdiff >= 70000 , 3, 
                          ifelse(Flow_Outlier %in% c("Tukey", "MAD") | Flowdiff < 1000, 2,
                                 "")),
         Comment_FM = ifelse(Flag_FM %in% c(2,3), "FM", ""),
         FlowdiffAdj = ifelse(Flag_FM == 3 | Comment_SAMP == "FM", median.Flowdiff_s * SetTime, Flowdiff))
```


Summarize number of outliers flagged
```{r}
FlowmeterQAQC$Flag_FM <- ordered(FlowmeterQAQC$Flag_FM)
print("Flowmeter Outliers")
summary(factor(FlowmeterQAQC$Flag_FM))
print("Sampling Outliers")
summary(factor(FlowmeterQAQC$Flag_SAMP))
print("Lab Outliers")
summary(factor(FlowmeterQAQC$Flag_LAB))
```

23. Plot changes and flags
```{r}

outlierPreFlow <- ggplot(FlowmeterQAQC, aes(x = factor(Month), y = Flowdiff,  text = paste('Date: ', Date,'<br>Inundation: ', Inundation2, '<br>Set time: ', SetTime), color = factor(Flag_FM))) + geom_point(size = 2.5, alpha = 0.5) +  scale_color_viridis(discrete = TRUE) + labs(title = "Flowmeter Pre-QC") +
  facet_wrap(~Station) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

ggplotly(outlierPreFlow)

outlierPostFlow <- ggplot(FlowmeterQAQC, aes(x = factor(Month), y = FlowdiffAdj, color = factor(Flag_FM))) + geom_point(size = 2.5, alpha = 0.5) + scale_color_viridis(discrete = TRUE)  + labs(title = "Flowmeter Post-QC") +
  facet_wrap(~Station) +   
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

grid.arrange(outlierPreFlow, outlierPostFlow, nrow = 2)
```

24. Plot before and after for SAMP
```{r}
outlierPreSamp <- ggplot(Flow.outlier, aes(x = factor(Month), y = Flowdiff, color = factor(Flag_SAMP))) + geom_point(size = 3, alpha = 0.8) + scale_color_viridis(discrete = TRUE) + labs(title = "Sampling Pre-QC") +
  facet_wrap(~Station) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

outlierPostSamp <- ggplot(FlowmeterQAQC, aes(x = factor(Month), y = FlowdiffAdj, color = factor(Flag_SAMP))) + geom_point(size = 3, alpha = 0.8) + scale_color_viridis(discrete = TRUE) + labs(title = "Sampling Post-QC") +
  facet_wrap(~Station) + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

grid.arrange(outlierPreSamp, outlierPostSamp, nrow = 2)
```


## QAQC: CPUE

25. Calculate Vol and CPUE, Vol_adj, CPUEAdj

```{r}
NetArea = 0.4572 * 0.25
FlowQAQC_CPUE <- FlowmeterQAQC %>%
  mutate(Volume = ifelse(FlowMeterSpeed == "Regular",
                         Flowdiff * 26873 * NetArea/999999,
                         ifelse(FlowMeterSpeed == "Low",
                                Flowdiff * 57560 * NetArea/999999, NA))) %>%
  filter(!is.na(Flowdiff)) %>%
  mutate(CPUE= round(Count/Volume,3))%>%
    
  mutate(VolumeAdj = ifelse(FlowMeterSpeed == "Regular",
                         FlowdiffAdj * 26873 * NetArea/999999,
                         ifelse(FlowMeterSpeed == "Low",
                                FlowdiffAdj * 57560 * NetArea/999999, NA))) %>%
  mutate(CPUEAdj = round(Count/VolumeAdj,3))%>%
  arrange(Datetime)

```

26. Look at distribution of CPUE values
```{r}
FlowQAQC_CPUE$Month <- factor(FlowQAQC_CPUE$Month)
FlowQAQC_low <- filter(FlowQAQC_CPUE, CPUE < 10)
FlowQAQC_high <- filter(FlowQAQC_CPUE, CPUE > 10)

# Histogram of values
CPUEHist <- ggplot(FlowQAQC_CPUE, aes(CPUEAdj)) + geom_histogram(binwidth = 1) +
  facet_wrap(~Station) + theme_bw()

# SHR vs STTD boxplot
CPUEBox <- ggplot(FlowQAQC_CPUE) + geom_boxplot(aes(x = Station, y = CPUEAdj)) + theme_bw()

# SHR vs STTD boxplot by month
CPUEBoxMonth <- ggplot(FlowQAQC_CPUE) + geom_boxplot(aes(x = Month, y = CPUEAdj, color = Month)) + facet_wrap(~Station) + scale_color_viridis(discrete = TRUE) + theme_bw() 

grid.arrange(CPUEHist, CPUEBox)

# SHR vs STTD boxplot by year
CPUEBoxYear <- ggplot(FlowQAQC_CPUE) + geom_boxplot(aes(x = factor(WY), y = CPUEAdj)) + facet_grid(Station~.) + theme_bw() 
ggplotly(CPUEBoxYear)

grid.arrange(CPUEBoxMonth, CPUEBoxYear)

```

CPUE and Count Plots
```{r fig.width = 10, fig.height = 8}
# Species
inv_summary <-FlowQAQC_CPUE %>%
  filter(WY>1998) %>%
  group_by(Station, WYClass, TaxonName) %>%
  summarize(median.CPUE = median(CPUEAdj),
            max.CPUE = max(CPUEAdj),
            max.Count = max(Count),
            median.Count = median(Count),
            total.CPUE = sum(CPUEAdj),
            n = n()) %>%
  filter(n > 2)

# All CPUE
speciesCPUE <- ggplot(FlowQAQC_CPUE, aes(TaxonName, CPUEAdj)) + 
  geom_jitter(aes(col = WYClass)) + facet_grid(Station~.) + 
  scale_color_viridis(discrete=TRUE) +
    theme_bw() + theme(axis.text = element_text(size = 12),
                      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15)) 

ggplotly(speciesCPUE)

# Median CPUE
species2 <- ggplot(inv_summary, aes(TaxonName, median.CPUE)) + geom_jitter(aes(col = WYClass)) + facet_grid(Station~.) + 
    scale_color_viridis(discrete=TRUE) + 
    theme_bw() + theme(axis.text = element_text(size = 12),
                      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

# MaxCPUE
species3 <- ggplot(inv_summary, aes(TaxonName, max.CPUE)) + geom_jitter(aes(col = WYClass)) + facet_grid(Station~.) + 
    scale_color_viridis(discrete=TRUE) + 
    theme_bw() + theme(axis.text = element_text(size = 12),
                      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))


# Median Count
medCount <- ggplot(inv_summary, aes(TaxonName, median.Count)) + geom_jitter(aes(col = WYClass)) + facet_grid(Station~.) + 
    scale_color_viridis(discrete=TRUE) + 
    theme_bw() + theme(axis.text = element_text(size = 12),
                      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

# Max Count
maxCount <- ggplot(inv_summary, aes(TaxonName, max.Count)) + geom_jitter(aes(col = WYClass)) + facet_grid(Station~.) + 
    scale_color_viridis(discrete=TRUE) + 
    theme_bw() + theme(axis.text = element_text(size = 12),
                      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

grid.arrange(species2, species3)
grid.arrange(medCount, maxCount)

# Which are the outliers?
ggplotly(maxCount)
```


27. Check on and change any known errors
```{r}
checkCounts <- filter(FlowQAQC_CPUE, Count>1000)
# Match up with datasheet 

checkCPUE <- filter(FlowQAQC_CPUE, CPUEAdj > 100)
checkCPUE2 <- filter(FlowQAQC_CPUE, is.na(CPUEAdj))
```

28. Look at summary table of adjusted CPUE values
```{r, eval = FALSE}
### Table of values
CPUE.adj.table <- FlowQAQC_CPUE %>%
  group_by(Station, FlowMeterSpeed, WYClass, TaxonName) %>%
  summarize(min.CPUE = min(CPUEAdj),
            median.CPUE = median(CPUEAdj),
            max.CPUE = max(CPUEAdj),
            n = n())

CPUE.adj.table %>%
    kbl() %>%
  kable_styling()

```

29. Determine and apply flags and cutoffs
    * In this case, used plots to decide to flag CPUE values > 70 

30. Add comment about what was flagged (Comment_CPUE = CPUE)
```{r}
CPUEQAQC <- FlowQAQC_CPUE %>%
  mutate(Flag_CPUE = ifelse(CPUEAdj>70, 2, "" ),
         Comment_CPUE = ifelse(CPUEAdj>70, "CPUE", ""))
```

31. Plot outliers
```{r}
outlier2a <- ggplot(CPUEQAQC, aes(x = Month, y = CPUE, color = Flag_FM)) + geom_point(size = 2.5, alpha = 0.5) + scale_color_viridis(discrete = "TRUE") + facet_wrap(~Station) + labs(title = "CPUE calculated with original Flowmeter values") + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

outlier2b <- ggplot(CPUEQAQC, aes(x = Month, y = CPUEAdj, color = Flag_CPUE)) + geom_point(size = 2.5, alpha = 0.5) + scale_color_viridis(discrete = "TRUE") + facet_wrap(~Station) +   labs(title = "CPUE calculated with adjusted Flowmeter values + CPUE flags") + 
  theme_bw() + theme(axis.text = element_text(size = 14),
                     axis.title = element_text(size =14),
                     legend.text = element_text(size = 14),
                     legend.title = element_text(size = 14), 
                     strip.text = element_text(size = 15))

ggplotly(outlier2b)

grid.arrange(outlier2a, outlier2b)

```

## Clean up display of dataset
32. Join taxa and clean up order of variables
```{r}
# Rename some columns, remove unnecessary columns
inv_select <- CPUEQAQC %>%
  dplyr::rename(Inundation = Inundation2,
         FlagPhys = Flag_PQC,
         FlagSamp = Flag_SAMP,
         FlagLab = Flag_LAB,
         FlagFM = Flag_FM, 
         FlagCPUE = Flag_CPUE,
         CommentPhys = Comment_PQC,
         CommentSamp = Comment_SAMP,
         CommentLab = Comment_LAB,
         CommentFM = Comment_FM,
         CommentCPUE = Comment_CPUE) %>%
  select(c(event_id, Datetime, Station,
           WY, WYClass, Inundation,
           WeatherCode, Tide, MicrocystisVisualRank,
           WaterTemperature:Turbidity,
           ConditionCode,FieldComments, 
           SetTime, FlowMeterSpeed, FlowMeterStart, FlowMeterEnd, Flowdiff, FlowdiffAdj, Volume, VolumeAdj,LabComments, Category, TaxonName, LifeStage, Count, CPUE, CPUEAdj, FlagPhys, CommentPhys, FlagSamp, CommentSamp, FlagLab, CommentLab, FlagFM, CommentFM, FlagCPUE, CommentCPUE)) 

# Modify some taxa to join correctly
inv_select$TaxonName[inv_select$TaxonName == "affinis"]  <- "Gambusia affinis" 
inv_select$TaxonName[inv_select$TaxonName == "Hydrachnidae"]  <- "Hydrachnidia" 
inv_select$LifeStage[inv_select$TaxonName == "Actinopterygii - eggs"]  <- "eggs"
inv_select$TaxonName[inv_select$TaxonName == "Actinopterygii - eggs"]  <- "Actinopterygii" 

############## CHECK
# Join taxa table with the rest of the data
inv_all <- left_join(inv_select, tax) %>%
  filter(!is.na(TaxonName))

# Rearrange 
inv_arrange <- inv_all %>% 
  select(c(event_id:Turbidity, SetTime:VolumeAdj, ConditionCode:FieldComments, LabComments:Category, OrganismID, TaxonRank, TaxonName, LifeStage:CommentCPUE))

```

33. Merge flags and commments into one flag, one comment column, replace "" with NA
```{r}
empty_as_na <- function(x){
    if("factor" %in% class(x)) x <- as.character(x) ## since ifelse wont work with factors
    ifelse(as.character(x)!="", x, NA)
}

inv_final <- inv_arrange %>%
  mutate(LifeStage = replace(LifeStage, LifeStage == "N/A", NA)) %>%
  mutate(across(c(FlagSamp:CommentCPUE), list(empty_as_na)) ) %>%
  select(-c(FlagSamp:CommentCPUE)) %>%
  rename(FlagSamp = FlagSamp_1, 
         FlagLab = FlagLab_1,
         FlagFM = FlagFM_1,
         FlagCPUE = FlagCPUE_1,
         CommentSamp = CommentSamp_1, 
         CommentLab = CommentLab_1,
         CommentFM = CommentFM_1,
         CommentCPUE = CommentCPUE_1) %>%
  mutate(QCFlags = paste(FlagSamp, " ", FlagLab, " ", FlagFM, " ", FlagCPUE)) %>%
  mutate(QCComments = paste(CommentSamp, " ", CommentLab, " ",CommentFM, " ",  CommentCPUE)) %>%
  relocate(FlowMeterSpeed, .before = "FlowMeterStart")

## Filter rows with a 7
threes <- inv_final%>%
  filter(grepl("3", QCFlags ))
```

34. Calculate proportion of data flagged
```{r}
## Amount replaced
print(paste0(round(nrow(threes)/nrow(inv_final)*100,3), "% highly suspicious"))
```

35. Write file

```{r, eval = FALSE}
# Write File
# quote = TRUE important for EML writing
today = format(today(),"%Y%m%d")
write.csv(inv_final, paste0("R_write/Drift/Drift_data_", today, ".csv"), row.names = FALSE, quote = TRUE)

```

36. Write R-markdown file