---
title: "Ichthyo_QAQC"
author: "Lisa Vance"
date: "2024-02-13"
output: html_document
editor_options: 
  chunk_output_type: console
---
YBFMP Ichtyoplankton Data 1998 - 2022

```{r set-options, echo=FALSE, cache=FALSE}

options(width = 10000)
```

## Setup

1. Set up and load libraries

```{r setup, results=FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

library(tidyverse)
library(dplyr)
library(ggplot2)
library(knitr)
library(gridExtra)
library(stringr)
library(plotly)
library(viridis)
library(kableExtra)
library(lubridate)
library(readxl)
library(readr)
library(anytime)
library(magrittr)
library(janitor)
library(tidylog)
```

2. Load data and check variable types
Note data is in both MS Access and MS Excel
Physical data is shared between drift and ichthyo since tows are done at the same time and site

```{r load, results = FALSE, warning = FALSE, message = FALSE}

################# bring in qa/qc physical data #################################
PhysData <-read_csv("drift data/LT_phys_qc_20240118.csv")

######### Read in Access catch data ###########################################

CatchData <- read_csv("ichthyo data/TblLarvalCatchDataAccess.csv")
Species <- read_csv("ichthyo data/TblLarvalLookUpV2.csv")
SamplingData <- read_csv("ichthyo data/TblLarvalSampAccess.csv")
IEPFish <- read_csv("ichthyo data/IEP FISH CODE.csv")

########## Read in Excel Catch data ###########################################

IchLabData <- read_csv("ichthyo data/IchLabExcelData.csv", skip=1)

######## Bring in Inundation data and Water Year type Data ###################
wy <- read_csv("WaterYearType_CDEC.csv") 
inundation <- read_csv("Yolo_Bypass_Inundation_1998-2022.csv")

```

3. Rename some columns and drop any unnecessary columns
```{r filter, results = FALSE, message = FALSE, warning = FALSE}

Species <- Species %>%
  rename (SpeciesCode = "Code",
          CommonName = "Species",
          ScientificName = "Scientific Name")
View(Species)

SamplingData <- SamplingData %>%
  rename (SamplingQAQCByAccess = "QA/QC'dBy",
          SamplingEnteredByAccess = 'EnteredBy',
          FieldCommentsLarval = "FieldComments") %>%
  select(-c(SamplingEnteredByAccess, SamplingQAQCByAccess))
View(SamplingData)

IEPFish <- IEPFish %>%
  select(-c("...5":"...17"))
View(IEPFish)

PhysData <- PhysData %>%
  select(-c(MeterSetTime, FlowMeterStart, FlowMeterEnd, FlowMeterSpeed, ConditionCode))
#these flow meter values relate to drift data, not ichthyo

CatchData <- CatchData %>%
  rename(CommentsCatch = Comments)
#help distinguish comments columns

```

4. Adjust Channel Location Column in Access data; Combine QA/QC'd physical data with larval sampling data and rename those columns. In 2015 tows were done to determine if channel location created bias in sampling.
```{r}

CatchSpecies <- left_join(CatchData, Species)
View(CatchSpecies)

#using "center" as default if no channel location is specified as most tows are done as center of channel as possible following SOPs

CatchSpecies2 <- mutate(CatchSpecies, ChannelLocation = case_when(is.na(ChannelLocation) ~ "Center", TRUE ~ ChannelLocation))

IchSample <- left_join(PhysData, SamplingData, by = "PhysicalDataID")
View(IchSample)

# rename columns to help simplify before pivoting to simplify column names and make tidy

IchSample2 <- IchSample %>%
  rename(Start_MidWest = "LarvalStartMeter_Mid_West",
         End_MidWest = "LarvalEndMeter_Mid_West",
         Start_NearWest = "LarvalStartMeter_Near_West",
         End_NearWest = "LarvalEndMeter_Near_West",
         Start_MidEast = "LarvalStartMeter_Mid_East",
         End_MidEast = "LarvalEndMeter_Mid_East",
         Start_NearEast = "LarvalStartMeter_Near_East",
         End_NearEast = "LarvalEndMeter_Near_East",
         Start_MidBottom = "LarvalStartMeter_Mid_Bottom",
         End_MidBottom = "LarvalEndMeter_Mid_Bottom") %>%
  select(-c(StartTime, StopTime, "2ndStartTime_East", "2ndStopTime_East",
            Bottom_StartTime))
View(IchSample2)

#now use pivot longer to create separate columns of "meter start" and "location"

StartPivot <- pivot_longer(IchSample2,
                           cols = c(Start_MidWest, Start_NearWest,
                                    Start_MidEast, Start_NearEast,
                                    Start_MidBottom, LarvalStartMeter), 
                           names_to = c("TowLocation"),
                           values_to = c("StartValue"),
                           names_prefix = c("Start_"),
                           values_drop_na = TRUE) %>%
  select(-c(End_MidWest, End_NearWest,
            End_MidEast, End_NearEast, 
            End_MidBottom, LarvalEndMeter)) %>%
  mutate(TowLocation = case_when(TowLocation == "LarvalStartMeter" ~ "Center",
                                 TowLocation == "MidWest" ~ "Mid_West",
                                 TowLocation == "MidEast" ~ "Mid_East",
                                 TowLocation == "NearWest" ~ "Near_West",
                                 TowLocation == "NearEast" ~ "Near_East",
                                 TowLocation == "MidBottom" ~ "Bottom",
                                 TRUE ~ TowLocation))
View(StartPivot)

EndPivot <- pivot_longer(IchSample2,
                         cols = c(End_MidWest, End_NearWest,
                                  End_MidEast, End_NearEast,
                                  End_MidBottom, LarvalEndMeter), 
                         names_to = c("TowLocation"),
                         values_to = c("EndValue"),
                         names_prefix = c("End_"),
                         values_drop_na = TRUE) %>%
  select(-c(Start_MidWest, Start_NearWest,
            Start_MidEast, Start_NearEast, 
            Start_MidBottom, LarvalStartMeter)) %>%
  mutate(TowLocation = case_when(TowLocation == "LarvalEndMeter" ~ "Center",
                                 TowLocation == "MidWest" ~ "Mid_West",
                                 TowLocation == "MidEast" ~ "Mid_East",
                                 TowLocation == "NearWest" ~ "Near_West",
                                 TowLocation == "NearEast" ~ "Near_East",
                                 TowLocation == "MidBottom" ~ "Bottom",
                                 TRUE ~ TowLocation))
View(EndPivot)

Pivot1 <- left_join(StartPivot, EndPivot)
View(Pivot1)

Pivot3 <- filter(Pivot1, !is.na(LarvalDataID)) %>%
  left_join(CatchSpecies2, by = c("LarvalDataID", "TowLocation" = "ChannelLocation"))
View(Pivot3)

# larval code mainly utilized for linking things in access database, now that 
# things are linked, not necessary to keep so can be dropped here

IchAccess <- Pivot3 %>%
  filter(Station == "STTD" | Station == "SHR") %>%
  select(-c(LarvalCode.x, LarvalCode.y))
View(IchAccess)

# this ensures looking at data that is in access, not excel
# this means these larvaldataID are not affected by the data gap to address
# between access and excel
# some of these NA are "no catch" and not blanks - think about a solution? 110 values
# early data (i.e. 1998 -2003 not found via contractor data records...)

# narrow down how many can be confirmed "no catch" (2010 onward) versus
# how many must be marked as "no data" (2009 and earlier) due to not being able 
# to confirm with contractor data and verifying it's not an additional mistaken entry

viewNA <- filter(IchAccess, is.na(LarvalCatchID))
# some include the data gap between access and excel

viewAccessNA <- filter(viewNA, year(Date) < 2019)


AccessNA <- filter(viewAccessNA, year(Date) >= 2010 & year(Date) < 2019)
AccessNoData <- filter(viewAccessNA, year(Date) < 2010)

# now rename each group of data appropriately and ensure # replaced values equal to 
# what was narrowed down between the two date ranges
NOSpecimens = mutate(IchAccess, SpeciesCode = case_when(IchAccess$Date %in% viewAccessNA$Date & year(Date) >= 2010
                                                        & year(Date) < 2019 & is.na(SpeciesCode) ~ 
                                                          "NONE", TRUE ~ SpeciesCode))

NoData = mutate(NOSpecimens, SpeciesCode = case_when(IchAccess$Date %in% viewAccessNA$Date & year(Date) < 2010
                                                     & is.na(SpeciesCode) ~ "NODATA", TRUE ~ SpeciesCode))

IchAccessA <- NoData
#this should have a date/time column for ease of combining with excel data later on
```

5. Ensure Access data is in correct date/time format for later QA/QC
```{r}

str(IchAccess)
str(IchAccessA)


```



5. Now clean up the columns and formatting for the lab data that came back 2019 onward that is housed in Excel. This will eventually be combined with the data from Access so that the complete data set is in one data frame.
```{r}

IchLabData <- IchLabData %>%
  rename(Program = 'Measuring program short name',
         Date = 'Sampling Event Date',
         Time = 'Sampling Event Time',
         Station = 'Sampling Area Number',
         SamplingNumber = 'Sampling Event Number',
         SampleID = 'Sample ID',
         OrganismType = 'Observation Type Short Name',
         OrganismGroup = 'Attribute',
         ScientificName = 'Observable',
         TotalCountSpecies = 'Value...10',
         TL = 'Value...11',
         FL = 'Value...12',
         LifeStage = 'Value...13',
         LarvalLifeStage = '...14',) %>%
  filter(!is.na(Program)) %>%
  select(-c(SamplingNumber, SampleID, Program, OrganismType, OrganismGroup, Time))

#format date and time columns for ability to combine with Access data
IchLabData$Date<-as.Date(IchLabData$Date,"%m/%d/%Y")
IchLabData$Year <- year(IchLabData$Date)
IchLabData$Month <- month(IchLabData$Date)
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
IchLabData$MonthAbb <- mymonths[ IchLabData$Month ]
IchLabData$Datetime = paste(IchLabData$Date, IchLabData$Time)
IchLabData$Datetime <- ymd_hm(IchLabData$Datetime)
IchLabData$Time <- strptime(IchLabData$Time, format = "%H:%M", tz = "") %>%
  strftime(IchLabData$Time, format = "%H:%M:%S", tz = "", usetz = FALSE)
IchLabData$Time <- hms::as_hms(IchLabData$Time)z

IchLabData2 <- IchLabData %>%
  mutate(event_id = paste0(Station, "_", Datetime)) %>%
  relocate(event_id, Datetime)

#combine lab data with physical data in preparation for binding with Access
IchLabPhysData <- left_join(PhysData, IchLabData2) %>%
  filter(year(Date) > 2018)


#set up for the overlap of lab data in 2019 when databases shifted
LabGap <- IchLabData2 %>%
  filter(Date < "2020-02-24") %>%
  mutate(FL = as.numeric(FL))
View(LabGap)

```


6. filter Acess data for dates that overlap with Excel
```{r}
IchAccessFilter <- IchAccessA %>%
  filter(Date > "2019-04-15") %>%
  select(-c(TL, FL, ScientificName, SpeciesCode, Count,
            CommonName, Stage))

```



7. Update the species data frame to match updates to how the contractors ID species. 
```{r}
#per contractor form Menidia sp. = common name silverside
# between lab data in excel and lab data from access, add to the 
# species lookup table to cover everything for joining 

SpeciesUpdate <- Species %>%
  add_row(SpeciesCode = "UNSS" , CommonName = "silverside", ScientificName = "Menidia sp.") %>%
  add_row(SpeciesCode = "POM", CommonName = "Unid Crappie", ScientificName = "Pomoxis sp.") %>%
  add_row(SpeciesCode = "NONE", CommonName = "NoCatch", ScientificName = "No Catch") %>%
  add_row(SpeciesCode = "RAIKIL", CommonName = "Rainwater Killifish", ScientificName = "Lucania parva") %>%
  add_row(SpeciesCode = "KLF", CommonName = "Killifish", ScientificName = "Cyprinodontidae spp.")

SpeciesUpdate2 <- SpeciesUpdate %>%
  filter(!is.na(ScientificName)) %>%
  filter(SpeciesCode != "TSE") %>%
  filter(SpeciesCode != "ASE")

# removing TSE - threadfin shad eggs and ASE american shad eggs in this version 
# since it does not appear contractor has made a comment re: eggs
# also the "animal tissue, baby clam, etc" is removed since those NA don't match
# correctly when tied to the excel data
```


```{r}

```



```{r}

```






