---
title: "LTPhysicalData_QAQC"
author: "Catarina Pien"
date: "April 6 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

##Edited ___ L.Vance for publishing update

```{r set-options, echo=FALSE, cache=FALSE}
```


```{r set-options, echo=FALSE, cache=FALSE}
options(fig.width = 12)
rm(list=ls(all=TRUE))
```

## 1.Setup and Download libraries

```{r setup, results=FALSE, warning = FALSE, message = FALSE}

rm(list=ls(all=TRUE))

if(!require(tidyverse)) {install.packages("tidyverse")
  library(tidyverse)}
if(!require(lubridate)) {install.packages("lubridate")
  library(lubridate)}
if(!require(gridExtra)) {install.packages("gridExtra")
  library(gridExtra)}
if(!require(kableExtra)) {install.packages("kableExtra")
  library(kableExtra)}
if(!require(knitr)) {install.packages("knitr")
  library(knitr)}
if(!require(tidylog)) {install.packages("tidylog")
  library(tidylog)}

```


## 2. Plotting functions

```{r plotfunctions}

# Yearly boxplot, y = variable of interest
Yearbox <-  function(data,y) {
    y <- enquo(y)
  data %>%
    ggplot() +
    geom_boxplot(mapping = aes(Year,!! y,fill = StationCode)) +
    theme_bw() +
  scale_fill_manual(values = c("coral3", "lightseagreen"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        legend.position = "bottom")
}

# Monthly boxplot, y = variable of interest
Monthbox <-  function(data,y) {
    y <- enquo(y)
  data %>%
    ggplot() +
    geom_boxplot(mapping = aes(MonthAbb,!! y,fill = StationCode)) +
    theme_bw() +
  scale_fill_manual(values = c("coral3", "lightseagreen"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        legend.position = "bottom")
}

# Point plot by date. Y = Variable of interest
VisPoint <-  function(data,y) {
    y <- enquo(y)
  data %>%
    ggplot() +
    geom_point(mapping = aes(Datetime,!! y,col = StationCode), size = 2) +
    theme_bw() +
  scale_colour_manual(values = c("coral3", "lightseagreen"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11),
        legend.position = "bottom")
} 

# Histogram by Station, y = variable of interest, binwidth
VisHist <-  function(data,y, bin) {
    y <- enquo(y)
  data %>%
    ggplot() +
    geom_histogram(mapping = aes(!! y,col = StationCode),binwidth = bin, fill = "lightseagreen", colour = "lightgray") +
    facet_wrap(~StationCode, scales = "free_x") +
    theme_bw() +
  scale_colour_manual(values = c("coral3", "lightseagreen"))+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))
} 

# Plot date vs. variable of interest, specifically for Lisbon
PlotVars <- function(data,y) {
    y <- enquo(y)
  data %>%
    ggplot() +
    geom_point(mapping = aes(Datetime,!! y, col = StationCode)) +
    theme_bw() +
  scale_colour_manual(values = c("#F3B2FF", "#106E83", "#FFC971", "#BAFF87")) + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))
  }
```


## 3.Load Data, Check Variable Types

```{r load, results = FALSE, warning = FALSE, message = FALSE}

phys <- read_csv("drift data/TblPhysicalDataAccess.csv")
phys2 <- read_csv("drift data/DriftSampExcelData.csv", skip=1)
WQ <- read_csv("drift data/LTWQ2020on.csv", skip=1)

#get rid of NA in phys2 (data entry changed from Access to Excel in 2020), rename columns to be able to combine, clean up columns
#Water quality separated from physical data in Excel

phys2 <- phys2 %>%
  filter(!is.na(`Measuring program short name`)) %>%
    rename(Program = 'Measuring program short name',
         Date = 'Sampling Event Date',
         Time = 'Sampling Event Time',
         Station = 'Sampling Area Number',
         SamplingNumber = 'Sampling Event Number',
         PhysicalDataID = '...6',
         ConditionCode = 'Condition Code',
         SamplingAltered = 'Sampling Altered',
         MeterSetTime = 'Set Time',
         FlowMeterStart = 'Flow Meter Start',
         FlowMeterEnd = 'Flow Meter End',
         FlowMeter50Start = 'Flow Meter Start (50)',
         FlowMeter50End = 'Flow Meter End (50)',
         FlowMeterSpeed = 'Flow Meter Speed',
         PhysicalDataIDx = 'Physical Data ID',
         EnteredBy = 'Entered by',
         QAQCBy = "QAQC'd by",
         FieldComments = 'Field Comments',
         SampleVolume = 'Sample Volume',
         SubsampleNumber = 'Subsample Number',
         DilutionVolume = 'Dilution Volume',
         SlideCount = 'Slide Count',
         MeshSize = 'Observation Area Name',
         Observation = 'Observation Area Number',
         SpotNumber = 'Spot Number',
         SpotCode = 'Spot Code (original/duplicate)') %>%
  select(-c(PhysicalDataID, PhysicalDataIDx,
            FlowMeter50Start,FlowMeter50End,
            EnteredBy, QAQCBy, SpotCode, SpotNumber, Observation,
            '...27', '...28', '...29', '...30', '...31', '...32'))

#rename and cleanup columns for WQ
WQ <- WQ %>%
    filter(!is.na(`Measuring Program Name`)) %>%
    rename(Program = 'Measuring Program Name',
         Date = 'WDL SAM_COLLECTION_DATE',
         Time = 'Collection Time',
         Station = 'Station Name',
         StationNumber = 'Station Number',
         SamplingNumber = 'Sampling Number (event)',
         WaterTemperature = 'water.temp',
         SpCnd = 'sp.cond',
         DO = 'DO.probe',
         Turbidity = 'turb',
         Secchi = secchi,
         Conductivity = EC,
         SampleDate = `Sample Date`,
         SampleTime = `Sample Time`,
         SampleNumber = `Sample Number`,
         MicrocystisVisualRank = microcyst,
         VegetationRank = VegRank) %>%
  select(-c('Run Number', 'Run Name'))

# Add and change date and time formats
phys <- phys %>% mutate(Datetime = paste(Date, Time, sep = " "))
phys2 <- phys2 %>% mutate(Datetime = paste(Date, Time, sep = " "))
WQ <- WQ %>% mutate(Datetime = paste(Date, Time, sep = ""))

phys$Datetime <- mdy_hms(phys$Datetime)
phys$Date<- mdy(phys$Date)
phys$Time <- strptime(phys$Time, format = "%H:%M", tz = "") %>%
  strftime(phys$Time, format = "%H:%M:%S") 
phys$Year <- ordered(year(phys$Date))
phys$Month <- ordered(month(phys$Date))
mymonths <- c("Jan","Feb","Mar",
              "Apr","May","Jun",
              "Jul","Aug","Sep",
              "Oct","Nov","Dec")
phys$Tide <- as.factor(phys$Tide)
#add abbreviated month name
phys$MonthAbb <- mymonths[ phys$Month ]
#set order of months
phys$MonthAbb <-ordered(phys$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))
# str(phys)

#do the same with phys2 from Excel
phys2$Datetime <- mdy_hm(phys2$Datetime)
phys2$Date<- mdy(phys2$Date)
phys2$Year <- ordered(year(phys2$Date))
phys2$Month <- ordered(month(phys2$Date))
#add abbreviated month name
phys2$MonthAbb <- mymonths[ phys2$Month ]
#set order of months
phys2$MonthAbb <-ordered(phys2$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

#do the same with water quality from excel
WQ$Datetime <- mdy_hm(WQ$Datetime)
WQ$Date<- mdy(WQ$Date)
WQ$Year <- ordered(year(WQ$Date))
WQ$Month <- ordered(month(WQ$Date))
#add abbreviated month name
WQ$MonthAbb <- mymonths[ WQ$Month ]
#set order of months
WQ$MonthAbb <-ordered(WQ$MonthAbb,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

```

## 4.Check variables to include in QC, reorganize the data frame.
```{r filter, results = FALSE, message = FALSE, warning = FALSE}

summary(phys$PhysicalDataID)
unique(phys$`Station Code`)
unique(phys$Recorder) 
summary(phys$`Field Check`)
unique(phys$Tide) 

# Rename some columns, remove unnecessary columns, filter to only SHR, STTD
phys.s <- phys %>%
  rename(Secchi = SecchiDiskDepth,
         StationCode = `Station Code`,
         Conductivity = EC,
         YSI = `YSI #`) %>%
  select(-c(Recorder, `Field Check`, Crew, EnteredBy, "QA/QC'dBy",  
            LightData, DriftData, LarvalData, ZoopsData, `50_ZoopsData`, ChlData, PhytoData, NutrData,
            Comments, DataCorrectionComments, StartMeter, EndMeter, MeterSetTime)) %>%
  filter(StationCode == "SHR" | StationCode == "STTD")

#clean up columns, filter by program to only YBFMP or shared
WQ2 <- WQ %>%
  filter(Program == "YBFMP" | Program == "Shared") %>%
  select(-c(LabOrField, Recorder, `Field Check`, FieldChecker, Crew, 
            LightData, DriftData, LarvalData, `150_ZoopsData`, `50_ZoopsData`,
            PhytoData, ChlData, NutrData, EnteredBy, QAQCBy, SurfaceIrr,
            Depth1Irr, Depth2Irr, Depth3Irr, Depth4Irr, SubIrr1, SubIrr2, SubIrr3,
            SubIrr4, SampleNumber, SampleDate, SampleTime))

#combine phys2 and WQ so columns will line up with Access file

PhysWQ <- full_join(WQ2, phys2, by = c("Program", "Station", "SamplingNumber", "Date", "Time", "Datetime", "Year",
                                       "Month", "MonthAbb"))

#filter for ending Dec 2022

PhysWQ2 <- filter(PhysWQ, year(Date) < 2023)

#check column types before combining
str(phys.s)
str(PhysWQ2)

#make sure column types match

PhysWQ3 <- PhysWQ2 %>%
  mutate(Secchi = as.numeric(Secchi),
         WaterTemperature = as.numeric(WaterTemperature),
         DO = as.numeric(DO),
         SpCnd = as.numeric(SpCnd),
         Conductivity = as.numeric(Conductivity),
         pH = as.numeric(pH),
         MicrocystisVisualRank = as.numeric(MicrocystisVisualRank),
         VegetationRank = as.numeric(VegetationRank),
         Turbidity = as.numeric(Turbidity),
         YSI = as.numeric(YSI),
         StationNumber = as.numeric(StationNumber),
         SampleDate = as.Date(SampleDate),
         SampleTime = as_datetime(SampleTime),
         Time = as_datetime(Time))

# Combine phys data from Access with Phys data from Excel
phys_yolo <- bind_rows(phys.s, PhysWQ)
```

## 5.Look at observations in stations

```{r Stations, message = FALSE, warning = FALSE}

# summarize number of observations per year
sta.sum <- phys_yolo %>%
  group_by(StationCode, Year) %>%
  summarize(n = n())

# plot number of observations per station
ggplot(sta.sum, aes(Year, n, fill = StationCode)) + geom_bar(stat = "identity") +theme_bw() +
  scale_y_continuous(breaks = seq(0,300,20))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

# plot number of observations per year
ggplot(sta.sum, aes(StationCode, n, fill = Year)) + geom_bar(stat = "identity") +
    scale_y_continuous(breaks = seq(0,600,50))+
    theme_bw()+
    theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

```


## 6.Overview of Physical Data (All stations)

```{r WQ Plot, message = FALSE, warning = FALSE}

p.temp <- ggplot(phys_yolo, aes(Date, WaterTemperature)) + geom_point() + labs(y = "Water Temp(C)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.secchi <- ggplot(phys_yolo, aes(Date, Secchi)) + geom_point() + labs(y = "Secchi Depth(m)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.ec <- ggplot(phys_yolo, aes(Date, Conductivity)) + geom_point() + labs(y = "EC(useimens/cm)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.spc <- ggplot(phys_yolo, aes(Date, SpCnd)) + geom_point() + labs(y = "SpCnd(useimens/cm)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.pH <- ggplot(phys_yolo, aes(Date, pH)) + geom_point() + labs(y = "pH") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.do <- ggplot(phys_yolo, aes(Date, DO)) + geom_point() + labs(y = "DO(mg/L)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.turb <- ggplot(phys_yolo, aes(Date, Turbidity)) + geom_point() + labs(y = "Turbidity(NTU)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))

# Arrange plots together
grid.arrange(p.temp, p.ec, p.spc, p.secchi, p.turb, p.do, p.pH)

```


## 7.Summary Tables - Min and max of variables by station

```{r minmaxtables, message = FALSE, warning = FALSE}
# All database data
WQ.overall <- phys_yolo %>%
  group_by(StationCode) %>%
  summarize(min.temp = min(WaterTemperature, na.rm=T),
            max.temp = max(WaterTemperature, na.rm=T),
            min.Conductivity = min(Conductivity, na.rm=T),
            max.Conductivity = max(Conductivity,na.rm=T),
            min.SPC = min(SpCnd,na.rm=T),
            max.SPC = max(SpCnd,na.rm=T),
            min.Secchi = min(Secchi,na.rm=T),
            max.Secchi = max(Secchi,na.rm=T),
            min.Turbidity = min(Turbidity,na.rm=T),
            max.Turbidity = max(Turbidity,na.rm=T),
            min.pH = min(pH,na.rm=T),
            max.pH = max(pH,na.rm=T),
            min.DO = min(DO,na.rm=T),
            max.DO = max(DO,na.rm=T),
            n = n()) 

kable(t(WQ.overall)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```


##8. Plots - Yolo

```{r Yolo temperature plots, warning = FALSE, message = FALSE}
Yearbox(phys_yolo, WaterTemperature)
Monthbox(phys_yolo,WaterTemperature)
VisPoint(phys_yolo,WaterTemperature)
VisHist(phys_yolo, WaterTemperature, 5)

Yearbox(phys_yolo, Secchi)
Monthbox(phys_yolo,Secchi)
VisPoint(phys_yolo,Secchi)
VisHist(phys_yolo, Secchi, 0.5)


Yearbox(phys_yolo, Turbidity)
Monthbox(phys_yolo,Turbidity)
VisPoint(phys_yolo,Turbidity)
VisHist(phys_yolo, Turbidity, 20)

Yearbox(phys_yolo, DO)
Monthbox(phys_yolo,DO)
VisPoint(phys_yolo,DO)
VisHist(phys_yolo, DO, 1)

Yearbox(phys_yolo, Conductivity)
Monthbox(phys_yolo,Conductivity)
VisPoint(phys_yolo,Conductivity)
VisHist(phys_yolo, Conductivity, 20)

Yearbox(phys_yolo, SpCnd)
Monthbox(phys_yolo,SpCnd)
VisPoint(phys_yolo,SpCnd)
VisHist(phys_yolo, SpCnd, 20)

Yearbox(phys_yolo, pH)
Monthbox(phys_yolo,pH)
VisPoint(phys_yolo,pH)
VisHist(phys_yolo, pH, 1)

```


##9. Correlation Plots: TurbidityxSecchi, DOxTemp, ConductivityxSpCnd
```{r Correlations, message = FALSE, warning = FALSE}
sec.tur <- ggplot(phys_yolo, aes(x=Turbidity, y = Secchi)) + geom_point() + geom_smooth() +
  labs(title = "Secchi x Turbidity", x = "Turbidity (NTU)", y = "Secchi Depth (m)")+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

do.temp <- ggplot(phys_yolo, aes(x=WaterTemperature, y = DO)) + geom_point() + geom_smooth() +
  labs(title = "DO x Temp", x = "Water Temp (C)", y = "DO (mg/L)")+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

ec.spc <- ggplot(phys_yolo, aes(x= SpCnd, y = Conductivity )) + geom_point() + geom_smooth() +
  #labs(title = "Conductivity x SpCnd", x = "SpCnd (usiemens/cm)", y = "Conductivity (usiemens/cm)")+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

spc.ec <- ggplot(phys_yolo, aes(x=Conductivity, y = SpCnd)) + geom_point() + geom_smooth() +
  labs(title = "SpCnd x Conductivity", x = "Conductivity (usiemens/cm)", y = "SpCnd (usiemens/cm)")+
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(hjust=0.5),
        axis.text = element_text(size = 11), 
        axis.text.x = element_text(angle = 90, hjust = 1),
        axis.title = element_text(size = 12),
        legend.text = element_text(size = 11))

grid.arrange(sec.tur, do.temp, spc.ec, ec.spc)
```


## 10. Check against Lisbon data, this part can be slow
```{r Lisbon Check Yolo, message = FALSE, warning = FALSE}
#Sensors
  #Water Temp in F =25  (2008)
  #DO= 61  (2013)
  #Conductivity = 100  (2013)
  #pH =62   (2013)
  #Turbidity =27  (2013)

# Read files (came from cdec4gov)
LIS_WaterTemperature <- read_csv("Data/STA/LIS_25.csv")
LIS_DO <- read_csv("Data/STA/LIS_61.csv")
LIS_pH <- read_csv("Data/STA/LIS_62.csv")
LIS_Turb <- read_csv("Data/STA/LIS_27.csv")
LIS_EC <- read_csv("Data/STA/LIS_100.csv")
LIS_EC$`DATE TIME` <- mdy_hm(LIS_EC$`DATE TIME`)


LIS_WaterTemperature_ed <- LIS_WaterTemperature %>%
  select(5,6) %>%
  filter(VALUE<99998) %>%
  mutate(Temp_C = round((VALUE-32)*5/9,1))
LIS_DO_ed <- LIS_DO %>%
  select(5,6) %>%
  rename(DO = VALUE)
LIS_pH_ed <- LIS_pH %>%
  select(5,6) %>%
  rename(pH = VALUE)
LIS_Turb_ed <- LIS_Turb %>%
  select(5,6) %>%
  rename(Turbidity = VALUE)
LIS_EC_ed <- LIS_EC%>%
  select(5,6) %>%
  rename(Conductivity = VALUE)

# Merge variables together
a <- merge(LIS_DO_ed, LIS_Turb_ed, by = "DATE TIME")
b <- merge(a, LIS_EC_ed, by = "DATE TIME")
c <- merge(b, LIS_pH_ed, by = "DATE TIME")
LIS_WQ <- left_join(LIS_WaterTemperature_ed, c, by = "DATE TIME")

# str(LIS_WQ)
LIS_WQ$Time <- strftime(LIS_WQ$`DATE TIME`, format = "%H:%M:%S")
LIS_WQ$Date <- as.Date(LIS_WQ$`DATE TIME`)
LIS_WQ$Hour <- as.numeric(format(strptime(LIS_WQ$Time, "%H:%M:%S"), "%H"))

LIS_WQ_f <- LIS_WQ %>%
  rename(Datetime = `DATE TIME`,
         WaterTemperature = Temp_C) %>%
  dplyr::filter(Hour>06 & Hour<15) %>%
  dplyr::filter(WaterTemperature>0 & WaterTemperature<40) %>%
  dplyr::filter(Conductivity>0)%>%
  filter(DO>0)%>%
         filter(pH>0 & pH<14)%>%
         filter(Turbidity >0) %>%
  mutate(StationCode="LIS_RT") %>%
  select(1,3:7,9,11)

# Make plots
Temp <- ggplot(LIS_WQ_f, aes(Datetime, WaterTemperature)) + geom_point() + theme_bw()
DO <- ggplot(LIS_WQ_f, aes(Datetime, DO)) + geom_point() + theme_bw()
pH <- ggplot(LIS_WQ_f, aes(Datetime, pH)) + geom_point() + theme_bw()
Turb <- ggplot(LIS_WQ_f, aes(Datetime, Turbidity)) + geom_point() + theme_bw()
Conductivity <- ggplot(LIS_WQ_f, aes(Datetime, Conductivity)) + geom_point() + theme_bw()

grid.arrange(Temp, DO, pH, Turb, Conductivity, nrow = 2)

Yolo_WQ <- phys_yolo %>%
  select(c(Datetime, WaterTemperature, DO, Turbidity, Conductivity, pH, Date, StationCode))

WQ_large <- rbind(LIS_WQ_f, Yolo_WQ)
WQ_large$Year <- as.numeric(year(WQ_large$Date))
WQ_sub <- WQ_large %>%
  filter(Year>2001)
WQ_sub2 <- WQ_large %>%
  filter(Year>2006)
WQ_sub3 <- WQ_large %>%
  filter(Year>2010)

```

## 11. Plots with Lisbon-Yolo data
```{r Plots for LIS_Yolo, echo = FALSE, warning = FALSE, message = FALSE}

PlotVars(WQ_large, WaterTemperature)
PlotVars(WQ_large, Conductivity)
PlotVars(WQ_large, DO)
PlotVars(WQ_large, pH)
PlotVars(WQ_large, Turbidity)
```


## 12. QC data
```{r QC, warning = FALSE, message = FALSE}
# Edits to data
to_drop <- c(1575, 1631, 1632, 1722, 1724, 1867, 1308, 748)

# To change
phys_yolo$WaterTemperature[phys_yolo$PhysicalDataID == 688] <- 16.7 # Was Fahrenheit
phys_yolo$WaterTemperature[phys_yolo$WaterTemperature == 0.169] <- 16.9 # Decimal place
phys_yolo$Turbidity[phys_yolo$PhysicalDataID==680] <- 15.4 # Typo
phys_yolo$Turbidity[phys_yolo$PhysicalDataID==656] <- 94.2 # Typo
phys_yolo$Conductivity[phys_yolo$PhysicalDataID==748] <- 732 # Typo
phys_yolo$Conductivity[phys_yolo$PhysicalDataID==926] <- 1284 # Typo
phys_yolo$Conductivity[phys_yolo$PhysicalDataID==1847] <- 170 # Typo
phys_yolo$SpCnd[phys_yolo$PhysicalDataID==1140] <- 848 # Typo
phys_yolo$SpCnd[phys_yolo$PhysicalDataID==1139] <- 889 # Typo
phys_yolo$SpCnd[phys_yolo$PhysicalDataID==1847] <- 101 # Typo
phys_yolo$Secchi[phys_yolo$PhysicalDataID==708] <- NA # Previously 0, but actually was not taken
phys_yolo$Secchi[phys_yolo$PhysicalDataID==708] <- NA # Previously 0, but actually was not taken
phys_yolo$DO[phys_yolo$PhysicalDataID==1409] <- NA # Previously 0, but actually was not taken
phys_yolo$pH[phys_yolo$PhysicalDataID==1501] <- 7.92 # Typo


# One entry was not entered
phys_yolo$StationCode[phys_yolo$PhysicalDataID==1752] <- "STTD"
phys_yolo$Conductivity[phys_yolo$PhysicalDataID==1752] <- 530
phys_yolo$SpCnd[phys_yolo$PhysicalDataID==1752] <- 563
phys_yolo$Turbidity[phys_yolo$PhysicalDataID==1752] <- 16.5
phys_yolo$Tide[phys_yolo$PhysicalDataID==1752] <- "Ebb"
phys_yolo$Date[phys_yolo$PhysicalDataID==1752] <-as.Date("2018-09-27", format = "%Y-%m-%d")
phys_yolo$pH[phys_yolo$PhysicalDataID==1752] <- 8.13

# Formatting
phys_yolo$Time[phys_yolo$PhysicalDataID==401] <- hms("13:22:00")
phys_yolo$Time[phys_yolo$PhysicalDataID==1602] <- hms("13:50:00")

# Remove rows with no data
phys_yolo <- phys_yolo%>%
  filter(!PhysicalDataID %in% to_drop)

phys_yolo %>%
  filter(SpCnd>1500)

```


### 13. Flag Data
* Flag data 
* 3: Replaced (above changes, mostly typos)
* 2: Suspect data, based on plots, but not out of the realm of possibility, not confirmed in field data
* blank: Pass
* Include comment to say which variable is flagged/replaced.
```{r Flag, message = FALSE, warning = FALSE}
# Lists for flags and flag comments
# Modified data due to typos
modified <- c(688, 680, 656, 748, 926, 1847, 1140, 1139, 1847, 708, 1409, 1501, 1818)

# Flagged but not replaced
flag <-  c(899, 885, 1087, 1090, 1314, 1218, 602, 668, 841, 1187)

# Variable associated with flag
wtemp <- c(688, 1818)
turb <- c(680, 656, 885, 668, 841, 1187)
cond <- c(748, 926, 1847)
spc <- c(1140, 1139, 1847, 899, 1087)
sec <- c(708, 1090)
do <- c(1409, 1314, 1218)
ph <- c(1501)

# Adding Flag and Comment variables
phys_yolo_flag <- phys_yolo %>%
  mutate(Flag_PQC = ifelse(PhysicalDataID %in% modified, 3,
                           ifelse(PhysicalDataID %in% flag, 2, "")),
         Comment_PQC = ifelse(PhysicalDataID %in% wtemp, "WTEMP",
                              ifelse(PhysicalDataID %in% turb, "TURB",
                                     ifelse(PhysicalDataID %in% cond, "COND",
                                            ifelse(PhysicalDataID %in% spc, "SPC",
                                                   ifelse(PhysicalDataID %in% sec, "SECCHI",
                                                          ifelse(PhysicalDataID %in% do, "DO",
                                                          ifelse(PhysicalDataID %in% ph, "PH", ""))))))))

phys_yolo_flag$Flag_PQC <- as.factor(phys_yolo_flag$Flag_PQC)

```

## 14. Plot QCed data

```{r Plot edited data, message = FALSE, warning = FALSE, echo = FALSE}
#

cols = c("lightslategrey", "goldenrod2", "slateblue4")
p.temp <- ggplot(phys_yolo_flag, aes(Date, WaterTemperature, col = Flag_PQC)) + geom_point() + labs(y = "Water Temp(C)") + scale_colour_manual(values = cols)+
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.secchi <- ggplot(phys_yolo_flag, aes(Date, Secchi, col = Flag_PQC)) + geom_point() + labs(y = "Secchi Depth(m)") +
 scale_colour_manual(values = cols)+ theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.conductivity <- ggplot(phys_yolo_flag, aes(Date, Conductivity, col = Flag_PQC)) + geom_point() + labs(y = "Conductivity(useimens/cm)") +
  theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.spc <- ggplot(phys_yolo_flag, aes(Date, SpCnd, col = Flag_PQC)) + geom_point() + labs(y = "SpCnd(useimens/cm)") +
  scale_colour_manual(values = cols)+theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.ec <- ggplot(phys_yolo_flag, aes(Date, Conductivity, col = Flag_PQC)) + geom_point() + labs(y = "EC(useimens/cm)") +
  scale_colour_manual(values = cols)+theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.pH <- ggplot(phys_yolo_flag, aes(Date, pH, col = Flag_PQC)) + geom_point() + labs(y = "pH") +
  scale_colour_manual(values = cols)+theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.do <- ggplot(phys_yolo_flag, aes(Date, DO, col = Flag_PQC)) + geom_point() + labs(y = "DO(mg/L)") +
  scale_colour_manual(values = cols)+theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))
p.turb <- ggplot(phys_yolo_flag, aes(Date, Turbidity, col = Flag_PQC)) + geom_point() + labs(y = "Turbidity(NTU)") +
 scale_colour_manual(values = cols)+ theme_bw() + theme(axis.text = element_text(size = 10), axis.title = element_text(size = 11))

# Arrange plots together
grid.arrange(p.temp, p.ec, p.spc, p.secchi, p.turb, p.do, p.pH, ncol = 2)


```

### 15. Replace blanks
```{r Write file, message = FALSE, warning = FALSE}

# Replace blanks with NA
empty_as_na <- function(x){
    if("factor" %in% class(x)) x <- as.character(x) ## since ifelse wont work with factors
    ifelse(as.character(x)!="", x, NA)
}

phys_yolo_flag <- phys_yolo_flag %>%
  mutate_each(list(empty_as_na),5:20)


```


```{r, eval = FALSE}
# Write cleaned up file to be used later (merged with zooplankton, etc.)
today = format(today(),"%Y%m%d")
write.csv(phys_yolo_flag, paste0("R_write/LT_phys_qc_", today, ".csv"), row.names = FALSE)

```

